---
title: "imagiveyoucrabs"
format: html
editor: visual
execute: 
  echo: FALSE
---
In these figures we attempt to show that crab carapace changes based on lattitude. in the graph we are showing the distributions at each latitude. The table shows summary statistics of carapace size based on site location. thank you. thank you. 
```{r}
pacman::p_load("lterdatasampler", "tidyverse", "ggthemes","kableExtra")
```

```{r}


  

pacman::p_load("lterdatasampler", "tidyverse", "ggthemes")
```

```{r}
```

```{r}
#| fig-cap: "this is my caption"

ggplot(pie_crab, aes(size, latitude)) +
  geom_point(color = "#CCCCCC") +
  theme_solarized_2(light = FALSE)
```

```{r}
crab_sub <- pie_crab %>% 
  group_by(site) %>% 
  summarize(crab_mean = round(mean(size),2),
            crab_sd = sd(size),
            crab_count = n()) 

crab_sub |> 
  kable(col.names = c("Site", "Crab Mean (mm)", "Crab STD (mm)", "Crab Count")) |> 
  kable_material_dark()


```
Horst A, Brun J (2023). _lterdatasampler:
  Educational Dataset Examples from the Long Term
  Ecological Research Program_. R package version
  0.1.1,
  <https://CRAN.R-project.org/package=lterdatasampler>.


